### 2013-05-14 report/reportmd.Rmd
Moved report scripts to own folder

**Location data**
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
locLevelInfo(.dat$data)
```

@@

```{r fig.height=8, fig.width=8, echo=FALSE, warning=FALSE, message=FALSE}
makePlotPanel(d$data, .study, pdf=FALSE, quiet=TRUE)
```

>>>>

**Location data**
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
options(width =160)
locLevelInfo(.dat$data)
```

@@

```{r fig.height=8, fig.width=8, echo=FALSE, warning=FALSE, message=FALSE}
makePlotPanel(alldata$data, .study, pdf=FALSE, quiet=TRUE)
```
